### 2024-01-30 ms.qmd
Updates

@@

```{r, fig-results}
#| label: figdeli
#| fig.cap: "Deli"
# First step, create the Intercepts for all models
## 1) Associative task
### Group = red
int_dar_CORTCold <- deli_red$b_Intercept
int_dar_ControlCold <- (deli_red$b_cortControl + deli_red$b_Intercept)
int_dar_CORTHot <- (deli_red$b_tempHot + deli_red$b_Intercept)
int_dar_ControlHot <- (deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept)
### Group = blue
int_dab_CORTCold <- deli_blue$b_Intercept
int_dab_ControlCold <- (deli_blue$b_cortControl + deli_blue$b_Intercept)
int_dab_CORTHot <- (deli_blue$b_tempHot + deli_blue$b_Intercept)
int_dab_ControlHot <- (deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)

@@

Model formula for task is:  
Choice  ~ Trial*cort*temp + (1 + Trial|lizard_id)  
Plots for the different models of the associative task:  
1.- _L. delicata_  
  1.a.- Red  
```{r , plotmod_dar, out.width="70%", fig.align="center"}
plot(mod_dar)
bayes_R2(mod_dar)
```
```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

  1.b.- Blue  
```{r , plotmod_dab, out.width="70%", fig.align="center"}
plot(mod_dab)
```

@@

2.- _L. guichenoti_  
  2.a.- Red  
```{r , plotmod_gar, out.width="70%", fig.align="center"}
plot(mod_gar)
```
```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

  2.b.- Blue  
```{r , plotmod_gab, out.width="70%", fig.align="center"}
plot(mod_gab)
```

>>>>

```{r, fig-results}
#| label: figdeli
#| fig.cap: "Deli"
source(here("R", "func.R"))
# First step, create the dfs for all models
## 1) L. delicata
### Red
df_del_red <- df_fig(as.data.frame(deli_red), "L. delicata", "Red")
### Blue
df_del_blue <- df_fig(as.data.frame(deli_blue), "L. delicata", "Blue")
## 2) L. guichenoti
### Red
df_gui_red <- df_fig(as.data.frame(guich_red), "L. guichenoti", "Red")
### Blue
df_gui_blue <- df_fig(as.data.frame(guich_blue), "L. guichenoti", "Blue")
#
# Second step, merge the df into a big Fig_df
Fig_df <- rbind(df_del_red, df_del_blue, df_gui_red, df_gui_blue) %>%
  mutate(Trial = gsub("X", "", Trial)) %>%
  mutate(Trial = as.numeric(Trial)) %>%
  rename("Predicted_prob" = "Value") %>%
data.frame()
write.csv(Fig_df, file= "./output/Checking/Fig_df.csv")
# Make the plot
figure_results <- plotting(Fig_df)
ggsave("./output/figures/figure_results.png", plot=figure_results, width = 18, height = 20, units = "cm", dpi = 3000)
print(figure_results)
```

@@

@@

Model formula for task is:  
Choice  ~ Trial*cort*temp + (1 + Trial|lizard_id)  
Plots for the different models of the associative task:  
1.- _L. delicata_  
  1.a.- Red  
```{r , plotmod_dar, out.width="70%", fig.align="center"}
bayes_R2(mod_dar)
plot(mod_dar)
```
```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

  1.b.- Blue  
```{r , plotmod_dab, out.width="70%", fig.align="center"}
bayes_R2(mod_dab)
plot(mod_dab)
```

@@

2.- _L. guichenoti_  
  2.a.- Red  
```{r , plotmod_gar, out.width="70%", fig.align="center"}
bayes_R2(mod_gar)
plot(mod_gar)
```
```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

  2.b.- Blue  
```{r , plotmod_gab, out.width="70%", fig.align="center"}
bayes_R2(mod_gab)
plot(mod_gab)
```
